Convergent Morphological Evolution in Squamate Reptiles
========================================================

This document includes all code required to generate the figures and results presented in our manuscript.

(1) load dependencies

```{r}
library(geometry)
library(geiger)
library(pcaMethods)
library(MASS)
library(TreeSim)
```

Get the trait data.

```{r}

# get trait data
sqMorphA<-read.csv("data/squamorph_v2.csv", na.strings=c("", " ", "."))

# pull out just continuously distributed characters
sqMorphContinuous<-sqMorphA[1:384, 4:26]

# pull out species names
species<-as.character(sqMorphA[1:384, 1])
```

Some of the names in 'species' don't match anything in the taxonomy for various reasons - mainly, they are outdated. The following lines substitute for some of the names. There are notes after each one. In some cases, the match is not exact - but all matches are close enough to place species in the correct clade for our analyses.

```{r}

#manual translation of outdated names
altSpecies<-species
altSpecies[species=="Cosymbotus"]<-"Hemidactylus craspedotus" # former monotypic genus
altSpecies[species=="Gecko"]<-"Gekko albofasciolatus" # arbitrary
altSpecies[species=="Geckonia"]<-"Tarentola chazaliae" # former monotypic genus
altSpecies[species=="Microscalabo"]<-"Lygodactylus bivittis" # former monotypic genus
altSpecies[species=="Palmatogecko"]<-"Pachydactylus vanzyli" # former genus w 2 species
altSpecies[species=="Tenuidactylu"]<-"Cyrtopodion caspium" # not sure what happened here
altSpecies[species=="Teratolepis"]<-"Hemidactylus albofasciatus" # small genus absorbed into hemidac?
altSpecies[species=="Chamaeleojax"]<-"Trioceros jacksonii" # reclassified
altSpecies[species=="Chamaeleorhi"]<-"Furcifer rhinoceratus" # has to be? rhi?
altSpecies[species=="amphibbarbat"]<-"Pogona barbata" # I am pretty sure these three are correct
altSpecies[species=="amphibisolep"]<-"Ctenophorus isolepis" #
altSpecies[species=="amphibnuchal"]<-"Ctenophorus nuchalis" #
# I think "Stellio" is correct - the listed species has a synonym of Stellio stellio
altSpecies[species=="Sator"]<-"Sceloporus angustus" #
altSpecies[species=="Scelopmagist"]<-"Sceloporus magister" #
altSpecies[species=="Scelopoccide"]<-"Sceloporus occidentalis" #
altSpecies[species=="Sceloporussi"]<-"Sceloporus rufidorsum" # I have no idea what this might be, but it's in the right genus at least
altSpecies[species=="Aperopristis"]<-"Leiosaurus catamarcensis" # old name
altSpecies[species=="Aptycholaemu"]<-"Anisolepis longicauda" # old name
altSpecies[species=="Chamaeleolis"]<-"Anolis chamaeleonides" # old name
altSpecies[species=="Chamaelinoro"]<-"Anolis barbouri" # old name
altSpecies[species=="Phenacosauru"]<-"Anolis bellipeniculus" # old name
altSpecies[species=="Ophryoessoid"]<-"Stenocercus caducus" # old name
altSpecies[species=="Proctotrectu"]<-"Stenocercus pectinatus" # old name - might be something else
altSpecies[species=="Tropidurusto"]<-"Tropidurus torquatus" # 
altSpecies[species=="Sauresia"]<-"Celestus agasepsoides" # old name
altSpecies[species=="Wetmorena"]<-"Celestus haetianus" # i think this is exact
altSpecies[species=="Pelamis"]<-"Hydrophis curtus" # 
altSpecies[species=="Python"]<-"Python molurus" # 
altSpecies[species=="Zaocys"]<-"Ptyas fusca" # 
altSpecies[species=="Aporosaura"]<-"Meroles anchietae" # exact
altSpecies[species=="Meroles"]<-"Meroles ctenodactylus" # choosing different species
altSpecies[species=="Cabrita"]<-"Ophisops leschenaultii" # old genus
altSpecies[species=="Lacertalep"]<-"Timon lepidus" # must be correct, a real trick
altSpecies[species=="Platyplacopu"]<-"Takydromus intermedius" # 
altSpecies[species=="Anops"]<-"Amphisbaena acrobeles" # 
altSpecies[species=="Leposternon"]<-"Amphisbaena cerradensis" # 
altSpecies[species=="Pantodactylu"]<-"Cercosaura quadrilineata" # 
altSpecies[species=="Prionodactyl"]<-"Cercosaura argulus" # 
altSpecies[species=="Anotis"]<-"Nannoscincus gracilis" # could be other things but all lygosomines
altSpecies[species=="Apterygodon"]<-"Dasia vittata" # only hit
altSpecies[species=="Riopa"]<-"Ablepharus pannonicus" # honestly no idea - tons of things
altSpecies[species=="Siaphos"]<-"Saiphos equalis" # 
altSpecies[species=="Trachydosaur"]<-"Tiliqua rugosa" # 
altSpecies[species=="Fitzsimonsia"]<-"Typhlacontias brevipes" # I think - locality matches, seems right
altSpecies[species=="Typhlacontia"]<-"Typhlacontias gracilis" # Random different species in genus
altSpecies[species=="Neoseps"]<-"Plestiodon reynoldsi" # 
altSpecies[381]<-"Platysaurus capensis" # just choosing a different species
altSpecies[384]<-"Lygosoma albopunctata" # just choosing a different species
```

We now use the taxonomy from Burbrink and Pyron to assign our specimens to clades. 

```{r}

# read in the taxonomy file
tnrs<-read.csv("data/squam_TNRS.csv")

# assign family, subfamily
# spMatchForFamily saves the species used for the matching assignment
family<-character(length=length(altSpecies))
subfam<-character(length=length(altSpecies))
spMatchForFamily<-character(length=length(altSpecies))
for(i in 1:length(altSpecies)) {
  mm<-agrep(altSpecies[i], tnrs[,2])
	if(length(mm)>0) {
		aa<-adist(altSpecies[i],tnrs[mm,2], partial=T)
		md<-which(aa[1,]==min(aa[1,]))
		spMatchForFamily[i]<-as.character(tnrs[mm,2][md[1]])
		family[i]<-as.character(tnrs[mm,3][md[1]])
		subfam[i]<-as.character(tnrs[mm,4][md[1]])
	}
}

cbind(species, altSpecies, spMatchForFamily, subfam, family)

```


